Predr_Cors

### 2023-02-01 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
draft for selected co-author circulation

---
title: "MS_Conclusion"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)`

>>>>

---
title: "MS_Conclusion"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
We have developed a framework for undertaking a MOSHEM in youth mental health and demonstrated its use by applying it to undertake a utility mapping study. We intend using this framework to undertake and synthesise multiple types of economic research. With further development the framework could be applied to extracting greater value from existing economic models in mental health and to facilitate collaborations between health economists and other stakeholders to address complex mental health modelling challenges. Although MOSHEMs provide a promising opportunity to advance the health economcis field, action from funders is required to realise this potential.

### 2023-02-01 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
draft for selected co-author circulation

However, having features that facilitate accountability, reuse and updating is not the same as being accountable, reused and updated. If diverse groups of stakeholders do not review model components, suggest improvements and develop alternatives, then little progress is made towards enhancing model legitimacy. Similarly, making code and data publicly available does not guarantee that others will know of the existence of these tools, trust their validity and find them easy to use. Without reuse, errors in model aretefacts are more likely to remain undetected. Even when errors are detected, they still need to be fixed, but maintaining code and data requires ongoing resourcing through a combination of centralised infrastructure and an active open source community.

To progress from a technical capability to behavioural outcomes, both our framework and MOSHEM need further work. Currently all the framework and model module libraries we have developed are available only as "development" releases. An early priority for us is to undertake the additional development, testing and documenting of these libraries so that we can submit production versions of each library to CRAN [@CRAN2022]. Making R libraries available on CRAN is normally a prerequisite for high levels of reuse.

The transferability claims we make for our existing modules are to date supported only by example programs using toy data. Our future work aims to address this with real world studies that apply modules to different concepts and contexts. Our current work program also aims to create new ready4 modules for modelling help-seeking choice, spatial epidemiology, household populations and primary mental health services that we hope will provide others with more reasons to use ready4 and contribute to its development. To facilitate code contributions by third parties, our libraries for authoring modules [@ready4pack2022: @ready4fun2022; @ready4use2022] require some additional development to make them easier to use by third parties without knowledge of the naming and directory strucuture conventions we use in authoring code.

<!-- Real applications would be better given importance. -->

## Implications for economic modelling in mental health
Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. We are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022]. Of the known barriers to adoption of open source models by health economists (including issues like intellectual property and confidentiality [@Pouwels2022; @Wu2019]), our experience suggests that the biggest challenges may be the enormous effort required to first prepare model code and data for public release in formats that facilitate appropriate reuse by third parties and to then maintain and contunually improve potentially large numbers of digital artefacts.

Automated tools such as those we developed in our modelling toolkit can help reduce the burden associated with some of these tasks. However, we think the current low rates of adoption by health economists of open source approaches [@Emerson2019; @Michalczyk2018; @Feenstra2022] (which in turn facilitate the collaboration that make modular models more attractive) will only change slowly unless there is significant and strategic investments made by research funders. Currently, the incentive structures for health economists do not promote dedicating large quantities of time to enabling peers to reuse their work.

Reducing waste in research is a responsibility of research funders [@chalmers2014increase] and the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017], limited reusability [@Emerson2019; @Michalczyk2018; @Feenstra2022] and uncertain validity [@Ghabri2019; @Radeva2020] of health economic models is wasteful. Approximately 4,000 mental health focused economic evaluation reports were produced between 2000 to 2019 [@RN34]. The intellectual asset represented by this literature could be very substantial if many of the models described in these reports could be brought and kept up to date and made available in formats that maximised transferability to diverse decision contexts. We believe that modular and open source approaches would be well suited to accomplishing this goal and that the framework we have developed could act as an early prototype for solving some of the technical challenges of this task. Ideally such a programme of research would be resourced to be sustained over the medium to long term and to engage a diverse network of investigators, contributors and advisers from high, middle and low income countries.

In addition to extracting more value from the existing health economic knowledge base in mental health, there is an opportunity for research funders to shape how future health economic models in mental health are undertaken. Mental health topics accounted for about 268 of 2829 (10%) peer reviewed economic evaluations undertaken during 26 month period in 2012-2014 identified in a previous review [@pitt2016economic]. There is also likely to a substantial annual output of economic research in mental health that focuses on the other 11 domains identified by Wagstaff and Culyer [@wagstaff2012four].

Providing adequate levels of funding to support MOSHEMs, fostering skills, supplying infrastructure (t)

<!-- Resilience of open source project needs multiple maintainers -->

@@

<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->
<!-- http://hdl.handle.net/1893/27205--><!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." --

<!-- the framework represents a technical capacity rather than a behavioural outcome.  -->

@@

 <!-- - One shot at big changes -->
 <!-- - Our analysis - do it in stages, be transparent, continually improve, get help, be flexible (modelling toolkit / monolithic model), have a framework -->
 <!-- A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->

<!-- Is it desirable for this to become default authoring tool or better to be replication tool. -->

Estimating the potential uptake of these tools is difficult.

<!-- Add ref to NMHSMN in Australia --> Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised, implemented and have practical utility as decision aids [@Zabell2021; @SQUIRES2016588].

- Community building (feasibility)
<!-- Open source is more than open access (limited discussion). -->
- Funding contingent directions - replications / transfers

<!-- Diversify skills - move to tools means software engineering, -->
<!-- More collaboration -->
<!-- Role for SIGs -->
<!-- Make grant proposals that give funders the opportunity to fund this work. -->
<!-- Share some code and data at small scale. -->

## Implications for health economists
<!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->
<!-- As modelling methods have become more sophisticated, some have argued that more complex models are required to adequately explore certain types of public health topics [@SQUIRES2016588].  -->
<!-- Modellers should be faithful to reaity and values of users DOI: 10.1002/asi.23697 -->
<!-- transferability - [https://doi.org/10.1017/S026646232200321X].  -->
Output by health economists [@pitt2016economic; @wagstaff2012four; @munoz2020health]

## Implications for research funders
<!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->
>

- unreasonable to expect more accountability without more resources

@@

Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.

The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.

@@

 <!-- as part of the Open Value Initiative [@Jansen2019].  -->

 <!-- Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].  -->
<!-- The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of climate change [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems. To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorders [@RN11].  -->

>>>>

However, having features that facilitate accountability, reuse and updating is not the same as being accountable, reused and updated. If diverse groups of stakeholders do not review model components, suggest improvements and develop alternatives, then little progress is made towards enhancing model legitimacy. Similarly, making code and data publicly available does not guarantee that others will know of the existence of these tools, trust their validity and find them easy to use. Without reuse, errors in model artefacts are more likely to remain undetected. Even when errors are detected, they still need to be fixed, but maintaining code and data requires ongoing resourcing through a combination of centralised infrastructure and an active open source community.

To progress from a technical capability to behavioural outcomes, both our framework and MOSHEM need further work. Currently all the framework and model module libraries we have developed are available only as "development" releases. An early priority for us is to undertake the additional development, testing and documenting of these libraries so that we can submit production versions of each library to CRAN [@CRAN2022]. Making an R library available on CRAN is normally a prerequisite for a high level of use.

The transferability claims we make for our existing modules are to date supported only by example programs using toy data. Our future work aims to address this with real world studies that apply modules to different concepts and contexts. Our current work program also aims to create new ready4 modules for modelling help-seeking choice, spatial epidemiology, household populations and primary mental health services that we hope will provide others with more reasons to use ready4 and contribute to its development. To facilitate code contributions by third parties, our libraries for authoring modules [@ready4pack2022: @ready4fun2022; @ready4use2022] require some additional development to make them easier to use by third parties without knowledge of the naming and directory structure conventions we use in authoring code.

## Implications for economic modelling in mental health
Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. We are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022]. Of the known barriers to adoption of open source models by health economists (including issues like intellectual property and confidentiality [@Pouwels2022; @Wu2019]), our experience suggests that the biggest challenges may be the enormous effort required to first prepare model code and data for public release in formats that facilitate appropriate reuse by third parties and to then maintain and continually improve potentially large numbers of digital artefacts.

Automated tools such as those we developed in our modelling toolkit can help reduce the burden associated with some of these tasks. However, we think the current low rates of adoption by health economists of open source approaches [@Emerson2019; @Michalczyk2018; @Feenstra2022] (which in turn facilitate the collaboration that make modular models more attractive) will only change slowly unless there is significant and strategic investments made by research funders. Currently, incentive structures for health economists do not promote the dedication of large quantities of time to enable peers to reuse their work.<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->

Reducing waste in research is a responsibility of research funders [@chalmers2014increase] and the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017], limited reusability [@Emerson2019; @Michalczyk2018; @Feenstra2022] and uncertain validity [@Ghabri2019; @Radeva2020] of health economic models is wasteful. Approximately 4,000 mental health focused economic evaluation reports were produced between 2000 to 2019 [@RN34]. The intellectual asset represented by this literature could be enhanced if many of the models described in these reports could be brought and kept up to date and made available in formats that maximised transferability to diverse decision contexts. We believe that modular and open source approaches would be well suited to accomplishing this goal and that the framework we have developed could act as an early prototype for solving some of the technical challenges of this task. Ideally such a program of research would be resourced to be sustained over the medium to long term and to engage a diverse network of investigators, contributors and advisers from high, middle and low income countries.

In addition to extracting more value from the existing health economic knowledge base in mental health, there is an opportunity for research funders to shape how future health economic models in mental health are undertaken. Mental health topics accounted for 268 of the 2829 (10%) peer reviewed economic evaluations undertaken during 26 month period in 2012-2014 identified by a review [@pitt2016economic]. The ongoing annual output of economic research in mental health that focuses on the other 11 domains identified by Wagstaff and Culyer [@wagstaff2012four] is probably also substantial. Funders should provide support for the projects and infrastructure to promote greater collaboration, interoperability, transferability and maintenance of future mental health modelling projects.

@@

Ideally health economists would explore these complex topics in partnership with modellers from other disciplines (in particular epidemiology and health services research) and a wide range of stakeholders such as other researchers, policymakers, service planners and community members. Modular and open source approaches would facilitate such investigations by breaking down ambitious and long term goals into manageable time-bound discrete projects, each progressed by different teams. To facilitate such an approach, a common framework of standards and tools would be needed. To be suitable for such a task our framework would need additional development, with its overall architecture reviewed for scalability and suitability and to provide better integration with and use of other open source languages (particularly python) and repositories. Whatever MOSHEM infrastructure is developed, its resilience would depend on a community of open source contributors sufficiently large and active to ensure that all core modules are maintained even after their original authors cease their involvement.

## General issues for health economists and health research funders
Some of the issues we have discussed in the context of the development of our model or health economic modelling in mental health are potentially relevant to health economists and funders of health economic research more generally. Proactive measures by funders to encourage more accountable, reusable and updatable health economic models is not a need confined to mental health. For example, funders have been encouraged to support methodological innovation to improve model transferability [@craig2018taking]. However, funders also need credible proposals to support and this is an area for health economists interested in MOSHEMs to prioritize. Health economists could use existing and new special interest groups to identify opportunities and enablers of more collaborative approaches to model development, potentially as the basis for future funding proposals.

Adopting MOSHEMs will expand the type of skillset typically engaged in health economic modelling projects, with a much greater role for data-scientists, software engineers and online community builders. The requirement for these roles should be incorporated into project proposals. Not all efforts by health economists to promote MOSHEMs need to depend on the decisions of research funders. Releasing selected subsets of unmaintained model artefacts in open source repositories is still better than not providing access to any code and data and can typically be accomplished within existing project budgets. Developing knowledge and skills of MOSHEMS can be advanced by making small contributions (e.g. improvements to documentation, code contributions) to open source projects. Our project website [@rfwn2022] includes details of multiple ways to contribute to ready4.

<!-- Estimating the potential uptake of these tools is difficult.  -->
<!-- Open source is more than open access (limited discussion). -->
 <!-- A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->
<!-- http://hdl.handle.net/1893/27205--><!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." --

@@

 <!-- - One shot at big changes -->
 <!-- - Our analysis - do it in stages, be transparent, continually improve, get help, be flexible (modelling toolkit / monolithic model), have a framework -->
<!-- Diversify skills - move to tools means software engineering, -->
<!-- More collaboration -->
<!-- Role for SIGs -->
<!-- Make grant proposals that give funders the opportunity to fund this work. -->
<!-- Share some code and data at small scale. -->

<!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->
<!-- As modelling methods have become more sophisticated, some have argued that more complex models are required to adequately explore certain types of public health topics [@SQUIRES2016588].  -->
<!-- Modellers should be faithful to reaity and values of users DOI: 10.1002/asi.23697 -->
<!-- transferability - [https://doi.org/10.1017/S026646232200321X].  -->
<!-- Output by health economists [@pitt2016economic; @wagstaff2012four; @munoz2020health] -->
<!-- - Can develop guidelines and funding proposals, make small amounts of artefacts online -->

<!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->

@@

<!-- Major mental health reform programs, <!-- such as those currently being implemented in Victoria, Australia [@VicRC2021],  -->
<!-- can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives.   -->

<!-- The development, validation and updating of more complex mental health economic models implemented over longer time frames may be too onerous a burden for a single modelling team.  -->

@@

 <!-- as part of the Open Value Initiative [@Jansen2019].  -->
<!-- Similarly, developing partnerships between modellers and decision-makers across the life-cycle of a modelling project can help ensure models are appropriately conceptualised, implemented and have practical utility as decision aids [@Zabell2021; @SQUIRES2016588]. -->
 <!-- Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].  -->
<!-- The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of climate change [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems. To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorders [@RN11].  -->

### 2023-02-01 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
draft for selected co-author circulation

Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them for out of sample prediction [@Kearns2013]. Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data. However, great care must be exercised when publicly releasing model aretefacts  derived from data on human subjects as they may by default embed a copy of the source dataset. Sensitive dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release. Another way to make MOSHEMs easier to use is to develop simple user-interfaces for non-technical users.

>>>>

Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them for out of sample prediction [@Kearns2013]. Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data. However, great care must be exercised when publicly releasing model artefacts derived from data on human subjects as they may by default embed a copy of the source dataset. Sensitive dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release. Another way to make MOSHEMs easier to use is to develop simple user-interfaces for non-technical users.

### 2023-02-01 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
edits up to mid discussion
draft for selected co-author circulation

There is a strong case for making health economists more accountable for the appropriate use and social acceptability of their models. Users of models should be able to assess their adequacy for a particular purpose [@thompson2019escape].  This goal is difficult to achieve in the current context of the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017] and frequently insufficient validation [@Ghabri2019] of health economic models. Many health economic models are released with undeclared errors [@Radeva2020]. The value judgments that strongly shape health economic analyses are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey]. A modelling team's value judgments about what questions to address, the most important features of a system to represent and the weighting of different types of evidence may be poorly aligned with those of the people impacted by decisions informed by model analyses [@thompson2022escape]. As health economic models adopt more sophisticated techniques, the need for accountability grows. More complex models may be more prone to propagation errors [@Saltelli2019] and models designed to address multiple questions should be expected to meet more onerous verification and validation obligations [@Eddy2012; @Feenstra2022]. The nature and extent of individual model authorship contributions may be less clear in models implemented over longer time-frames with a large and changing group of collaborators [@thompson2022escape].

@@

Our interest in modular and open source source approaches developed when we began seeking am appropriate framework for undertaking and validly synthesising diverse types of economic research in mental health. Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019]. Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge [@RN22;@RN23]. A substantial economic literature already exists to assess the affordability and value for money of mental health interventions [@RN34]. This economic evaluation work is an essential prerequisite for improving allocative efficiency in mental health, but could be of greater value to systems planners if integrated with a broader program of economic research.

>>>>

There is a strong case for making health economists more accountable for the appropriate use and social acceptability of their models. Potential users of models should be able to assess their adequacy for a particular purpose [@thompson2019escape].  This goal is difficult to achieve in the current context of the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017] and frequently insufficient validation [@Ghabri2019] of health economic models. Many health economic models are released with undeclared errors [@Radeva2020]. The value judgments that strongly shape health economic analyses are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey]. A modelling team's value judgments about what questions to address, the most important features of a system to represent and the weighting of different types of evidence may be poorly aligned with those of the people impacted by decisions informed by model analyses [@thompson2022escape]. As health economic models adopt more sophisticated techniques, the need for accountability grows. More complex models may be more prone to propagation errors [@Saltelli2019] and models designed to address multiple questions should be expected to meet more onerous verification and validation obligations [@Eddy2012; @Feenstra2022]. The nature and extent of individual model authorship contributions may be less clear in models implemented over longer time-frames with a large and changing group of collaborators [@thompson2022escape].

@@

Our interest in modular and open source approaches developed when we began seeking am appropriate framework for undertaking and validly synthesising diverse types of economic research in mental health. Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019]. Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge [@RN22;@RN23]. A substantial economic literature already exists to assess the affordability and value for money of mental health interventions [@RN34]. This economic evaluation work is an essential prerequisite for improving allocative efficiency in mental health, but could be of greater value to systems planners if integrated with a broader program of economic research.

### 2023-02-01 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
draft for selected co-author circulation

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r cpkgs, tab.cap='Modelling toolkit R packages for developing and using MOSHEMs that meet framework standards', tab.id = 'cpkgs', echo = F, results = 'asis'}
library(kableExtra)  
df <- tibble::tibble(Package = c("ready4",
                                       "ready4fun",
                                       "ready4class",
                                       "ready4pack",
                                       "ready4use",
                                       "ready4show"),
                           # Version = Package %>%
                           #   purrr::map_chr(~utils::packageDescription(.x) %>%
                           #                    purrr::pluck("Version")),
                           Focus = c("Foundation",
                                     "Module algorithms",
                                     "Module structures",
                                     "Module libraries",
                                     "Datasets",
                                     "Analyses"),
                           A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
                           R = c("4","5","4-5","1,3,6","3,7",""),
                           U = c("","","","1-3","1",""),
                           # E = c("", "1","1-2","1","3",""),
                           # L = c("","","","1,3","2-3",""),
                           # Y = c("","","","","","1-2"),
                           `Depends on` = Package %>%
                             purrr::map(~ {
                               utils::packageDescription(.x) %>%
                                 `[`(c("Depends", "Imports")) %>%
                                 purrr::map(~{
                                   if(is.null(.x)){
                                     character(0)
                                     }else{
                                       .x %>%
                                         strsplit(",\\n") %>%
                                         purrr::flatten_chr() %>%
                                         purrr::map(~strsplit(.x,", ") %>%
                                                      purrr::flatten_chr()) %>%
                                         purrr::flatten_chr() %>% sort() %>%
                                         purrr::discard(~startsWith(.x,"R "))
                                       }
                                   }) %>%
                                 purrr::flatten_chr() %>%
                                 unique() %>%
                                 sort() %>%
                                 purrr::map_chr(~{
                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
                                     unname()
                                   if(!is.na(problem_idx_1L_chr))
                                     updated_1L_chr <- updated_1L_chr %>%
                                     stringr::str_sub(end = problem_idx_1L_chr-1)
                                   updated_1L_chr %>% 
                                     trimws(which = "left") 
                                   })
                               }) %>% 
                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
  as.data.frame() 
    df$Ref <- c("@ready42022",
                    "@ready4fun2022",
                    "@ready4class2022",
                    "@ready4pack2022",
                    "@ready4use2022",
                    "@ready4show2022")
df <- df %>%
  dplyr::mutate(Standard = purrr::pmap_chr(df,
                                           ~paste0("A",
                                                  ..3,
                                                  paste0(rep("&nbsp;",
                                                      2+max(nchar(df[,3]))-nchar(..3)),
                                                      collapse = ""#
                                                      ),
                                                  ifelse(..4=="","","R"),
                                                  ..4,
                                                  paste0(rep("&nbsp;",
                                                      2+max(nchar(df[,4]))-nchar(..4)),
                                                      collapse = ""#
                                                      ),
                                                  ifelse(..5=="","","U"),
                                                  ..5,
                                                  paste0(rep("&nbsp;",
                                                      1+max(nchar(df[,5]))-nchar(..5)),
                                                      collapse = ""#
                                                      )#,
                                                  # ifelse(..6=="","","E"),
                                                  # ..6,
                                                  # paste0(rep("&nbsp;",
                                                  #     1+max(nchar(df[,6]))-nchar(..6)),
                                                  #     collapse = ""#
                                                  #     ),
                                                  # ifelse(..7=="","","L"),
                                                  # ..7,
                                                  # # paste0(rep("&nbsp;",
                                                  # #     1+max(nchar(df[,7]))-nchar(..7)),
                                                  # #     collapse = ""#
                                                  # #     ),
                                                  # ifelse(..8=="","","&nbsp; &nbsp; &nbsp; &nbsp; Y"),
                                                  # ..8,
                                                  # paste0(rep("&nbsp;",
                                                  #     1+max(nchar(df[,8]))-nchar(..8)),
                                                  #     collapse = ""#
                                                  #     )
                                                  ))) %>%

>>>>

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r cpkgs, tab.cap='Modelling toolkit R libraries for developing and using MOSHEMs that meet framework standards', tab.id = 'cpkgs', echo = F, results = 'asis'}
library(kableExtra)  
df <- tibble::tibble(Package = c("ready4",
                                       "ready4fun",
                                       "ready4class",
                                       "ready4pack",
                                       "ready4use",
                                       "ready4show"),
                           # Version = Package %>%
                           #   purrr::map_chr(~utils::packageDescription(.x) %>%
                           #                    purrr::pluck("Version")),
                           Focus = c("Foundation",
                                     "Module algorithms",
                                     "Module structures",
                                     "Module libraries",
                                     "Datasets",
                                     "Analyses"),
                           A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
                           R = c("4","5","4-5","1,3,6","3,7",""),
                           U = c("","","","1-3","1",""),
                           # E = c("", "1","1-2","1","3",""),
                           # L = c("","","","1,3","2-3",""),
                           # Y = c("","","","","","1-2"),
                           `Depends on` = Package %>%
                             purrr::map(~ {
                               utils::packageDescription(.x) %>%
                                 `[`(c("Depends", "Imports")) %>%
                                 purrr::map(~{
                                   if(is.null(.x)){
                                     character(0)
                                     }else{
                                       .x %>%
                                         strsplit(",\\n") %>%
                                         purrr::flatten_chr() %>%
                                         purrr::map(~strsplit(.x,", ") %>%
                                                      purrr::flatten_chr()) %>%
                                         purrr::flatten_chr() %>% sort() %>%
                                         purrr::discard(~startsWith(.x,"R "))
                                       }
                                   }) %>%
                                 purrr::flatten_chr() %>%
                                 unique() %>%
                                 sort() %>%
                                 purrr::map_chr(~{
                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
                                     unname()
                                   if(!is.na(problem_idx_1L_chr))
                                     updated_1L_chr <- updated_1L_chr %>%
                                     stringr::str_sub(end = problem_idx_1L_chr-1)
                                   updated_1L_chr %>% 
                                     trimws(which = "left") 
                                   })
                               }) %>% 
                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
  as.data.frame() 
if(params$X@outp_formats_chr[1] != "Word"){
      df$Ref <- c("@ready42022",
                    "@ready4fun2022",
                    "@ready4class2022",
                    "@ready4pack2022",
                    "@ready4use2022",
                    "@ready4show2022")
}else{
  df$Ref <- ""
}

df <- df %>%
  dplyr::mutate(Standard = purrr::pmap_chr(df,
                                           ~paste0("A",
                                                  ..3,
                                                  paste0(rep("&nbsp;",
                                                      2+max(nchar(df[,3]))-nchar(..3)),
                                                      collapse = ""#
                                                      ),
                                                  ifelse(..4=="","","R"),
                                                  ..4,
                                                  paste0(rep("&nbsp;",
                                                      2+max(nchar(df[,4]))-nchar(..4)),
                                                      collapse = ""#
                                                      ),
                                                  ifelse(..5=="","","U"),
                                                  ..5,
                                                  paste0(rep("&nbsp;",
                                                      1+max(nchar(df[,5]))-nchar(..5)),
                                                      collapse = ""#
                                                      )#,
                                                  # ifelse(..6=="","","E"),
                                                  # ..6,
                                                  # paste0(rep("&nbsp;",
                                                  #     1+max(nchar(df[,6]))-nchar(..6)),
                                                  #     collapse = ""#
                                                  #     ),
                                                  # ifelse(..7=="","","L"),
                                                  # ..7,
                                                  # # paste0(rep("&nbsp;",
                                                  # #     1+max(nchar(df[,7]))-nchar(..7)),
                                                  # #     collapse = ""#
                                                  # #     ),
                                                  # ifelse(..8=="","","&nbsp; &nbsp; &nbsp; &nbsp; Y"),
                                                  # ..8,
                                                  # paste0(rep("&nbsp;",
                                                  #     1+max(nchar(df[,8]))-nchar(..8)),
                                                  #     collapse = ""#
                                                  #     )
                                                  ))) %>%
